---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```


```{r, eval=TRUE, echo=FALSE}
# only running test cases for fulpw since usage info specific to owner
pgk_cov <- covr::package_coverage()
per_cov <- round(covr::percent_coverage(pgk_cov))
```



# GXPAinterface

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
`r  badger::badge_custom('codecov', paste0(per_cov,'%25'), color = 'green', url = 'https://covr.r-lib.org/')`
<!-- badges: end -->

## Overview

[{GXPAinterface}](https://biogit.pri.bms.com/pages/IOCT-discovery-preclin/GXPAinterface/) 
is an R package with various function to access GXPA API and collection of 
functions to pre-process the data for importing into GXPA.

 - Importing from GXPA:
   - `get_data_from_gxpa()` to import data from GXPA
   - `get_series_info_from_gxpa()` to series information from GXPA
 - Exporting to GXPA:
   -  get_GXPA_session_list()  to see all the sessions already on GXPA
   - `begin_new_session()` to create a session (staging area) on GXPA
   - `send_file_to_session()` to export a file to GXPA
   - `login_and_get_user_cookie()` to obtain user cookie needed to export to GXPA
   - `dry_run_session()` after you load files, you can do a dry run to make sure files are formatted properly. NOTE: this won't work until GXPA is upgraded to the python 3 version.
   -  load_session()  after your load files, you can run this to trigger the task to load data from the session to the SQL database.
 - File Preparation
   - `make_series_info_file()` to create a series information file
   - `check_files_for_GXPA()` to run many checks on expression data and metadata


## Installation

Install the released version of
[{GXPAinterface}](https://biogit.pri.bms.com/pages/IOCT-discovery-preclin/GXPAinterface/) 
from BMS RStudio Package Manager (BRAN):

```{r}
my_repos <- c(
  "BMS CRAN mirror" = "http://pm.rdcloud.bms.com:4242/prod-cran/latest",
  "BMS RSPM" = "http://pm.rdcloud.bms.com:4242/bms-cg-biogit-bran/latest"
)

install.packages("GXPAinterface", repos = my_repos)
```

Or install the development version from BMS BioGit with:

```{r}
remotes::install_github(
  repo = "IOCT-discovery-preclin/GXPAinterface", 
  host = "https://biogit.pri.bms.com/api/v3"
)
```

or:

```{r}
remotes::install_git(
  "https://biogit.pri.bms.com/IOCT-discovery-preclin/GXPAinterface.git"
)
```

## Note About Connecting to GXPA API

[{GXPAinterface}](https://biogit.pri.bms.com/pages/IOCT-discovery-preclin/GXPAinterface/) 
can make use of R environments for accessing the GXPA API. When importing from 
GXPA your GXPA API token must be provided, and when importing from GXPA your 
GXPA username and password must be provided. While is it possible to provide 
these each time the respective function is used, it is more convenient to set 
these for the current R session, or even set for all sessions.

To set the token and login information for the current session:

```{r}
Sys.setenv(GXPA_TOKEN = "MY_GXPA_USER_TOKEN")
Sys.setenv(GXPA_USERNAME = "MY_GXPA_USERNAME")
Sys.setenv(GXPA_PASSWORD = "MY_GXPA_PASSWORD")
```


More convenient is to set the following environment variables in a `.Renviron` file 
(`usethis::edit_r_environ()`):

```
GXPA_TOKEN  = MY_GXPA_USER_TOKEN
GXPA_USERNAME = MY_GXPA_USERNAME
GXPA_PASSWORD = MY_GXPA_PASSWORD
```

These environment variable values will be used automatically if defined in your R session.



## Code of Conduct
  
Please note that this project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.
