---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GXPAinterface

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->


## Installation

Install the released version of `{GXPAinterface}` from BMS RStudio Package Manager (BRAN):

```{r, eval = FALSE}
install.packages(
  "GXPAinterface", 
  repos = "http://pm.rdcloud.bms.com:4242/bms-cg-biogit-bran/latest"
)
```

Or install the development version from BMS BioGit with:

```{r, eval=FALSE}
remotes::install_github(
  repo = "IOCT-discovery-preclin/GXPAinterface", 
  host = "https://biogit.pri.bms.com/api/v3"
)
```

or:

```{r, eval=FALSE}
remotes::install_git(
  "https://biogit.pri.bms.com/IOCT-discovery-preclin/GXPAinterface.git"
)
```

## Example

EXAMPLE CODE TBD

```{r example}
library(GXPAinterface)
```



## Code of Conduct
  
Please note that the icWGCNA project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
